---
title: "problem3_datasetsolution"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
```

## Loading Data Employees

```{r cars}
Employee<-read.csv("Employee.csv")
str(Employee)
```
DOJ and DOL ,which are date of joining and leaving date for an employee needs to be converted into date format first
```{r}
library(lubridate)
Employee$DOJ<-as.Date(Employee$DOJ,"%d-%m-%Y")
Employee$DOL<-as.Date(Employee$DOL,"%d-%m-%Y")

```
creating a new variable which holds year for each employee DOJ

```{r}
Employee$Joining_Year<-year(Employee$DOJ)
Employee$Left_year<-year(Employee$DOL)
head(Employee)
```

Now we want to know number of employees after each year,
so the logic goes like this
             1.we calculate total number of employees, grouping by years,which is but first step towards                   solving.
             2.once we get number of employees in each year we take cumulative sum and this gives number                of employees at each year,we still didn't account for those who left
             3.In this part we group varaible date of leaving the firm by year and subtract from earlier
               cumulative sum and we are left with employees after each year.
```{r}
Number_of_employees<-Employee %>% group_by(Employee$Joining_Year) %>% summarise(n())
number_of_thoseleft<-Employee %>% group_by(Employee$Left_year) %>% summarise(n())
nn<-na.omit(number_of_thoseleft)
names(nn)<-c("year","numberofleft")

```

```{r}
#taking cumulative sum at each year

Number_of_employees$cumsum<-cumsum(Number_of_employees$`n()`)

#combining with number of employees left
forma<-cbind(Number_of_employees,nn[,2])

#employees left after each year
forma$Employeeleft_after_each_year<-forma$cumsum-forma$numberofleft

#employees attrition rate each year
forma$Attrition_Rate<-forma$numberofleft/forma$Employeeleft_after_each_year
forma[,c(1,5,6)]

```
In this part we will try find average Employee tenure after end of each year.
```{r}
head(Employee)
employee1<-Employee
employee1$diff_time<-employee1$DOL-employee1$DOJ
```

we will now ,group the variable difference in time based on year,which give us total number of days at each year and then we will divide who left each year,provide us the average tenure.

```{r}
average_tenure<-employee1 %>% group_by(employee1$Left_year) %>% summarize(averge=mean(diff_time,na.rm=T))
names(average_tenure)<-c("Year","Average_Employee_Tenure")

# This gives us average tenure after each year
```
Creating final table
```{r}
Employee_after_each_year<-forma$Employeeleft_after_each_year
Attrition_rate<-forma$Attrition_Rate
output<-cbind(average_tenure[1:9,],Employee_after_each_year,Attrition_rate)
output
```
The table provide us imformation about number of Employees at the end of each year,average tenure of employee and the attrition rate.
